\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[blue]{classic}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\usepackage[unicode]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname{Ivan}
\familyname{Andreev}
\address{}{Moscow, Russia}
\mobile{+7(925)***-****}
\email{ivandeex\,@\,gmail\,.\,com}
\homepage{https://about\,.\,ivandeex\,.\,com}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}
\maketitle

\section{Brief description}
\cvline{}{
  My main direction --- system development and testing.\newline{}
  My primary programming language --- Python.\newline{}
  I enjoy OpenSource software and tools I use for work and fun.
}

\section{Projects}
\subsection{C++}
\cvline{XxxSoft}{
  \url{http://www.xxx.com/product.html}\newline{}
  Xxx fork with security
}

\subsection{Python}
\cvline{Xxx4py}{
  \url{https://github.com/ivandeex/xxx4py}\newline{}
  Pure python Xxx library implementation
}

\section{Experience}
\cventry
  {Oct 2013 - present}
  {Software Engineer}
  {Freelance LLC}
  {}{}
  {
    Development and support of Database
  }
\cventry 
  {Dec 2009 - Sep 2013}
  {Software Engineer}
  {XxxSoft}
  {}{}
  {Query parsing, translating and processing\newline{}
   Client tools\newline{}
   Build system, packaging}

\section{Development skills}
\subsection{Programming Languages}
\cvlanguage{C++, C, Bash}{Expert}{}
\cvlanguage{Python, Xxx}{Intermediate}{}
\cvlanguage{LaTeX, Xxx}{Basic}{}
\subsection{Tools}
\cvline{}{gcc, gdb, git, svn, xxx}

\section{Computer skills}
\cvcomputer{IDE}{Eclipse, Xcode}{}{}
\cvcomputer{OS}{Linux (RedHat, Debian), Windows}{}{}

\section{Education}
\cventry
  {Sep 2004 -  Jul 2009}
  {Information Technology}
  {Moscow Institute of Physics and Technology, Moscow, Russia}
  {}{}
  {Engineer}

\section{Publications}
\cvline{}{Target-oriented distributed approach for X (rus)\newline{}
Andreev I.V. Proceedings of <<Scientific X (NC-2012)>>. 2012. \#3. Pp. 1-9.}
\cvline{}{Problems of optimization in X (rus)\newline{}
Andreev I.V. Algorithms, methods and systems of data processing. 2011. N1(28).}


\section{Links}
\cvline{Personal~page}{\url{https://about.ivandeex.com/}}
\cvline{LinkedIn}{\url{https://www.linkedin.com/in/ivandeex}}
\cvline{GitHub}{\url{https://github.com/ivandeex}}

\end{document}
